Secure Composition of Robust and Optimising Compilers

### 2023-06-18 popl/main.tex
Start blue

>>>>

\subsection{$\src{L_{\tmssafe}}$: A Temporal but Not Spatial Memory Safe Language}\label{subsec:ltms}
\begin{gather*}
  \begin{aligned}
    \mi{(Pre\text{--}Types)}~\src{\type[_{e}]}&\bnfdef\src{\natt} \mid \src{\ptrn} \hspace{0.5cm}
    \mi{(Pointer\ Qualifiers)}~\src{\ptrqual}\bnfdef\ \src{\fullq} \mid \src{\halfq} \hspace{0.5cm}
    \mi{(Types)}~\src{\type}\bnfdef\src{\type_{e}} \mid \src{\type_{e}\to\bot} \\
  \end{aligned}
\end{gather*}

\hltt{some type rules}

$\src{L_{\tmssafe}}$ is a statically typed language where each well-typed term is temporal memory safe.
To enforce this, the language marks pointers with respect to their ownership, where $\src{\fullq}$ means {\em owned} and $\src{\halfq}$ means {\em not owned}.
An owned pointer can only be used by a deallocation, whereas reads and writes must be done on non-owned pointers.
One can convert owned to non-owned pointers implicitly.
Syntactic constraints together with the type system ensure that non-owned pointers never ,,live'' longer than owned pointers.
For example, in an expression $\src{\llet{x}{\expr[_{1}]}{\expr[_{2}]}}$, if $y$ is a $\src{\wptr}$ in $\expr[_{1}]$, it must be a $\src{\ptr}$ in $\expr[_{2}]$.
